\textbf{\sc Deliberative Autonomy for Marine Robotics}

### 2012-01-23 trunk/arch.tex
Added figures -- from sutton book chapter froor now but I can  reedit them in the future

In T-REX architecture reactors have two core functions;
synchronization where the main focus is to track and refine the
evolution of the state of the world at any single tick, and
deliberation which focus on providing a plan to the agent in order to
complete the reactor {\em Internal} goals. These two processes are
intertwined in the sense that one influences the outcome of the
other. They are represented as two europa solvers modifying the same
plan database and for which the execution is managed by the T-REX 
framework rythemed by the time advance during the execuion of the
system:
\begin{enumerate}
\item The synchronization solver is a specialized eurpa solver that
  will integrate in the plan new information about the evolution of
  the External state varaible and ensure that the reactor propagate
  these in order yto both identify its current stetate and inform
  other reactors of any state change on its internal timelines. This
  solver is summoned at the beginnning of every single tick.
\item The deliberation solver is managing the deliberation process of
  the reactor in order to produce a new plan or alter its current plan
  as new goals are given to the reactor or the synchronization solver
  identifying a conflict between the current state of the world and
  the expectations of the previous plan. This process can  span other
  multiple tick and therrfore can be interrupted at any single tick in
  order for the synchronization solver to do its task.
\end{enumerate}

@@

>>>>

In T-REX architecture reactors have two core functions;
synchronization where the main focus is to track and refine the
evolution of the state of the world at any single tick, and
deliberation which focus on providing a plan to the agent in order to
complete the reactor {\em Internal} goals. These two processes are
intertwined in the sense that one influences the outcome of the
other. They are represented as two europa solvers modifying the same
plan database and for which the execution is managed by the T-REX 
framework as time advance during the execution of the system:
\begin{enumerate}
\item The synchronization solver is a specialized europa solver that
  will integrate in the plan new information about the evolution of
  the External state variable and ensure that the reactor propagate
  these in order to both identify its current state and inform
  other reactors of any state change on its internal timelines. This
  solver is summoned at the beginning of every single tick.
\item The deliberation solver is managing the deliberation process of
  the reactor in order to produce a new plan or alter its current plan
  as new goals are given to the reactor or the synchronization solver
  identifying a conflict between the current state of the world and
  the expectations of the previous plan. This process can  span other
  multiple tick and therefore can be interrupted at any single tick in
  order for the synchronization solver to do its task.
\end{enumerate}

While synchronization is assumed to be fast enough that it can be
resolved in less than a tick. Deliberation on the other hand can take
several ticks reflecting that automated planning can take time
depending on how far in the future the planner is looking ahead and
the complexity of the model. T-REX architecture, and more specifically
the europa based reactor in our case, takes this into account by
considering synchronization and deliberation as two concurrent tasks
with their own timing requirements and priority. 
While the two processes are separate, they share the same plan
internal to a reactor and therefore at every synchronization cycle the
planning process is informed of the new world state and its impact on
the plan. Conversely, when the planning process eventually finds a
solution, synchronization is informed about generating the planned
state values on the {\em external} state variables. This {\em
  external} plan defines the set of {\em goals} for this state
variable managed by another {\em reactor}. Fig. \ref{fig:tick-exec}
shows a conceptual view of these two tasks.

\begin{figure}[!htbp]
  \centering
  \vskip-1pc
  \includegraphics[width=0.55\columnwidth]{figs/tick-cycle}
  \caption{\small \texttt{T-REX} reactor execution cycle: {\em
      Deliberation} is interrupted by {\em synchronization} at the
    beginning of every {\em tick} allowing integration of state
    information.}
  \label{fig:tick-exec}
  \vskip-0.8pc
\end{figure}

@@

{\em fpy: I still wonder whether I should start with planning assuming
  first that the initial state is known and then develop
  synchronization and how it ties state information in to the plan or
  the other way around as it is now}
